---
title: "[CLIENT NAME] AdWords Performance"
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
---

```{r setup, include=FALSE}
# Libraries
library(RAdwords)
library(lubridate)
library(ggplot2)
library(tidyverse)
library(corrplot)
library(scales)
library(tidytext)
library(cowplot)

# Variables
googleAuth <- doAuth()
customerId <- Sys.getenv("CLIENT1ID")
availableBudget <- 30000
targetConversions <- 300

# Dates
yesterday = today() - days(1)
startOfCurrentMonth = today() - day(today()) + 1
endOfLastMonth = startOfCurrentMonth - 1 
starOfLastMonth = endOfLastMonth - days_in_month(endOfLastMonth) + 1
```
# Campaign performance
## Performance: Month-to-date

```{r campaign scatterplot 1, echo=FALSE, eval=FALSE}

chunk1_body <- statement(select=c('CampaignName','Conversions','CostPerConversion','Cost'),
                         report="CAMPAIGN_PERFORMANCE_REPORT",
                         where="Cost > 150000000",
                         start=startOfCurrentMonth,
                         end=yesterday)

chunk1_data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk1_body)

names(chunk1_data) <- c("Campaign", "Conversions", "CPA", "Cost")

ggplot(chunk1_data, aes(x = Cost, y = CPA, size = Conversions)) +
    geom_point() +
    geom_text(aes(label = Campaign))

```

## Performance: Last 30 days

```{r campaign scatterplot 2, echo=FALSE, eval=FALSE}

thirtyDaysAgo <- today() - days(30)

chunk2_body <- statement(select=c('CampaignName','Conversions','CostPerConversion','Cost'),
                         report="CAMPAIGN_PERFORMANCE_REPORT",
                         where="Cost > 150000000",
                         start=thirtyDaysAgo,
                         end=yesterday)

chunk2_data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk2_body)

names(chunk2_data) <- c("Campaign", "Conversions", "CPA", "Cost")

ggplot(chunk2_data, aes(x = Cost, y = CPA, size = Conversions)) +
    geom_point() +
    geom_text(aes(label = Campaign))

```

## Performance: Last 60 days

```{r campaign scatterplot 3, echo=FALSE, eval=FALSE}

sixtyDaysAgo <- today() - days(60)

chunk3_body <- statement(select=c('CampaignName','Conversions','CostPerConversion','Cost'),
                         report="CAMPAIGN_PERFORMANCE_REPORT",
                         where="Cost > 150000000",
                         start=sixtyDaysAgo,
                         end=yesterday)

chunk3_data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk3_body)

names(chunk3_data) <- c("Campaign", "Conversions", "CPA", "Cost")

ggplot(chunk3_data, aes(x = Cost, y = CPA, size = Conversions)) +
    geom_point() +
    geom_text(aes(label = Campaign))

```

## Performance: Last 90 days

```{r campaign scatterplot 4, echo=FALSE, eval=FALSE, eval=FALSE}

ninetyDaysAgo <- today() - days(90)

chunk4_body <- statement(select=c('CampaignName','Conversions','CostPerConversion','Cost'),
                         report="CAMPAIGN_PERFORMANCE_REPORT",
                         where="Cost > 150000000",
                         start=ninetyDaysAgo,
                         end=yesterday)

chunk4_data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk4_body)

names(chunk4_data) <- c("Campaign", "Conversions", "CPA", "Cost")

 ggplot(chunk4_data, aes(x = Cost, y = CPA, size = Conversions)) +
    geom_point() +
    geom_text(aes(label = Campaign))

```

# Metrics correlation plot

```{r correlation plot, echo=FALSE, eval=FALSE}

aYearAgo <- today() - days(365)

chunk5_body <- statement(select=c('Date','Clicks','Conversions','CostPerConversion',
                                  'Cost','ConversionRate','AverageCpc','Impressions','Ctr'),
                         report="ACCOUNT_PERFORMANCE_REPORT",
                         start=aYearAgo,
                         end=yesterday)

chunk5_data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk5_body)

corr <- cor(chunk5_data[,-1])

corrplot(corr, method = "pie", type = "upper")

```		
# Ad Scheduling Heatmaps

## Ad Scheduling: Impressions

```{r ad scheduling heatmap 1, echo=FALSE, eval=FALSE}

ninetyDaysAgo <- today() - days(90)

chunk6_body <- statement(select=c("DayOfWeek","HourOfDay","Impressions","Conversions","CostPerConversion","SearchImpressionShare"),
                         report="ACCOUNT_PERFORMANCE_REPORT",
                         start=ninetyDaysAgo,
                         end=yesterday)

chunk6_data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk6_body)

names(chunk6_data) <- c("DayOfWeek", "HourOfDay", "Impressions", "Conversions","CPA","SearchIS")

chunk6_data$HourOfDay <- factor(chunk6_data$HourOfDay, levels=c(0:23))
chunk6_data$DayOfWeek <- factor(chunk6_data$DayOfWeek, levels=c("Sunday","Saturday","Friday","Thursday","Wednesday","Tuesday","Monday"))

ggplot(chunk6_data, aes(x=HourOfDay, y=DayOfWeek, z=Impressions)) + geom_tile(aes(fill = Impressions)) +
    scale_fill_gradient(low="white", high="blue", labels=comma)

```

## Ad Scheduling: Search Impression Share

```{r ad scheduling heatmap 2, echo=FALSE, eval=FALSE}

ggplot(chunk6_data, aes(x=HourOfDay, y=DayOfWeek, z=SearchIS)) + geom_tile(aes(fill = SearchIS)) +
    scale_fill_gradient2(low="white", high="blue", labels=comma, midpoint=0.5)

```

## Ad Scheduling: Conversions

```{r ad scheduling heatmap 3, echo=FALSE, eval=FALSE}

ggplot(chunk6_data, aes(x=HourOfDay, y=DayOfWeek, z=Conversions)) + geom_tile(aes(fill = Conversions)) +
    scale_fill_gradient(low="white", high="blue", labels=comma)

```

## Ad Scheduling: CPA

```{r ad scheduling heatmap 4, echo=FALSE, eval=FALSE}

ggplot(chunk6_data[chunk6_data$CPA > 0,], aes(x=HourOfDay, y=DayOfWeek, z=CPA)) + geom_tile(aes(fill = CPA)) +
    scale_fill_gradient2(low="white", high="blue", labels=comma, midpoint=50)

```

# Search Terms N-Grams

```{r tidy search terms, echo=FALSE, eval=FALSE}

ninetyDaysAgo <- today() - days(90)
data(stop_words)

chunk7_body <- statement(select=c("Query","Clicks","Impressions","Conversions","Cost"),
                         report="SEARCH_QUERY_PERFORMANCE_REPORT",
                         start=ninetyDaysAgo,
                         end=yesterday)

chunk7_data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk7_body)

unigrams <- chunk7_data %>% unnest_tokens(word, Searchterm) %>% anti_join(stop_words) %>%
    group_by(word) %>%
    summarize(Clicks=sum(Clicks), Impressions=sum(Impressions), Conversions=sum(Conversions), Cost=sum(Cost),
              Ctr=sum(Clicks)/sum(Impressions), ConversionRate=sum(Conversions)/sum(Clicks), Cpa=sum(Cost)/sum(Conversions),
              AvgCpc = sum(Cost)/sum(Clicks))

bigrams <- chunk7_data %>% unnest_tokens(bigram, Searchterm, token="ngrams", n=2) %>% group_by(bigram) %>%
    summarize(Clicks=sum(Clicks), Impressions=sum(Impressions), Conversions=sum(Conversions),
              Cost=sum(Cost), Ctr=sum(Clicks)/sum(Impressions), ConversionRate=sum(Conversions)/sum(Clicks),
              Cpa=sum(Cost)/sum(Conversions), AvgCpc = sum(Cost)/sum(Clicks))

trigrams <- chunk7_data %>% unnest_tokens(trigram, Searchterm, token="ngrams", n=3) %>% group_by(trigram) %>%
    summarize(Clicks=sum(Clicks), Impressions=sum(Impressions), Conversions=sum(Conversions),
              Cost=sum(Cost), Ctr=sum(Clicks)/sum(Impressions), ConversionRate=sum(Conversions)/sum(Clicks),
              Cpa=sum(Cost)/sum(Conversions), AvgCpc = sum(Cost)/sum(Clicks))

```

## Unigrams

```{r unigrams, echo=FALSE, eval=FALSE}

pu_imp <- unigrams %>% top_n(10, Impressions) %>% ggplot(aes(y=Impressions, x=reorder(word, Impressions))) +
    geom_bar(stat = "identity") +
    coord_flip()

pu_clicks <- unigrams %>% top_n(10, Clicks) %>% ggplot(aes(y=Clicks, x=reorder(word, Clicks))) +
    geom_bar(stat = "identity") +
    coord_flip()

pu_ctr <- unigrams %>% filter(Clicks > 100) %>% top_n(10, Ctr) %>% ggplot(aes(y=Ctr, x=reorder(word, Ctr))) +
    geom_bar(stat = "identity") +
    coord_flip()

pu_cpc <- unigrams %>% filter(Clicks > 100) %>% top_n(10, AvgCpc) %>% ggplot(aes(y=AvgCpc, x=reorder(word, AvgCpc))) +
    geom_bar(stat = "identity") +
    coord_flip()

pu_cost <- unigrams %>% top_n(10, Cost) %>% ggplot(aes(y=Cost, x=reorder(word, Cost))) +
    geom_bar(stat = "identity") +
    coord_flip()

pu_conv <- unigrams %>% top_n(10, Conversions) %>% ggplot(aes(y=Conversions, x=reorder(word, Conversions))) +
    geom_bar(stat = "identity") +
    coord_flip()

pu_cpa <- unigrams %>% filter(Conversions > 1) %>% top_n(10, Cpa) %>% ggplot(aes(y=Cpa, x=reorder(word, Cpa))) +
    geom_bar(stat = "identity") +
    coord_flip()

pu_cr <- unigrams %>% filter(Conversions > 1) %>% top_n(10, ConversionRate) %>% ggplot(aes(y=ConversionRate, x=reorder(word, ConversionRate))) +
    geom_bar(stat = "identity") +
    coord_flip()

plot_grid(pu_imp, pu_clicks, pu_ctr, pu_cpc, pu_cost, pu_conv, pu_cpa, pu_cr, ncol=2)

```

## Bigrams

```{r bigrams, echo=FALSE, eval=FALSE}

pb_imp <- bigrams %>% top_n(10, Impressions) %>% ggplot(aes(y=Impressions, x=reorder(bigram, Impressions))) +
    geom_bar(stat = "identity") +
    coord_flip()

pb_clicks <- bigrams %>% top_n(10, Clicks) %>% ggplot(aes(y=Clicks, x=reorder(bigram, Clicks))) +
    geom_bar(stat = "identity") +
    coord_flip()

pb_ctr <- bigrams %>% filter(Clicks > 100) %>% top_n(10, Ctr) %>% ggplot(aes(y=Ctr, x=reorder(bigram, Ctr))) +
    geom_bar(stat = "identity") +
    coord_flip()

pb_cpc <- bigrams %>% filter(Clicks > 100) %>% top_n(10, AvgCpc) %>% ggplot(aes(y=AvgCpc, x=reorder(bigram, AvgCpc))) +
    geom_bar(stat = "identity") +
    coord_flip()

pb_cost <- bigrams %>% top_n(10, Cost) %>% ggplot(aes(y=Cost, x=reorder(bigram, Cost))) +
    geom_bar(stat = "identity") +
    coord_flip()

pb_conv <- bigrams %>% top_n(10, Conversions) %>% ggplot(aes(y=Conversions, x=reorder(bigram, Conversions))) +
    geom_bar(stat = "identity") +
    coord_flip()

pb_cpa <- bigrams %>% filter(Conversions > 1) %>% top_n(10, Cpa) %>% ggplot(aes(y=Cpa, x=reorder(bigram, Cpa))) +
    geom_bar(stat = "identity") +
    coord_flip()

pb_cr <- bigrams %>% filter(Conversions > 1) %>% top_n(10, ConversionRate) %>% ggplot(aes(y=ConversionRate, x=reorder(bigram, ConversionRate))) +
    geom_bar(stat = "identity") +
    coord_flip()

plot_grid(pb_imp, pb_clicks, pb_ctr, pb_cpc, pb_cost, pb_conv, pb_cpa, pb_cr, ncol=2)

```

## Trigrams

```{r trigrams, echo=FALSE, eval=FALSE}

pt_imp <- trigrams %>% top_n(10, Impressions) %>% ggplot(aes(y=Impressions, x=reorder(trigram, Impressions))) +
    geom_bar(stat = "identity") +
    coord_flip()

pt_clicks <- trigrams %>% top_n(10, Clicks) %>% ggplot(aes(y=Clicks, x=reorder(trigram, Clicks))) +
    geom_bar(stat = "identity") +
    coord_flip()

pt_ctr <- trigrams %>% filter(Clicks > 100) %>% top_n(10, Ctr) %>% ggplot(aes(y=Ctr, x=reorder(trigram, Ctr))) +
    geom_bar(stat = "identity") +
    coord_flip()

pt_cpc <- trigrams %>% filter(Clicks > 100) %>% top_n(10, AvgCpc) %>% ggplot(aes(y=AvgCpc, x=reorder(trigram, AvgCpc))) +
    geom_bar(stat = "identity") +
    coord_flip()

pt_cost <- trigrams %>% top_n(10, Cost) %>% ggplot(aes(y=Cost, x=reorder(trigram, Cost))) +
    geom_bar(stat = "identity") +
    coord_flip()

pt_conv <- trigrams %>% top_n(10, Conversions) %>% ggplot(aes(y=Conversions, x=reorder(trigram, Conversions))) +
    geom_bar(stat = "identity") +
    coord_flip()

pt_cpa <- trigrams %>% filter(Conversions > 1) %>% top_n(10, Cpa) %>% ggplot(aes(y=Cpa, x=reorder(trigram, Cpa))) +
    geom_bar(stat = "identity") +
    coord_flip()

pt_cr <- trigrams %>% filter(Conversions > 1) %>% top_n(10, ConversionRate) %>% ggplot(aes(y=ConversionRate, x=reorder(trigram, ConversionRate))) +
    geom_bar(stat = "identity") +
    coord_flip()

plot_grid(pt_imp, pt_clicks, pt_ctr, pt_cpc, pt_cost, pt_conv, pt_cpa, pt_cr, ncol=2)

```

# Impression Share analysis

```{r impression share, echo=FALSE, eval=FALSE}

ninetyDaysAgo <- today() - days(90)

chunk8_body <- statement(select=c("Date","AverageCpc","SearchRankLostImpressionShare","SearchBudgetLostImpressionShare",
                                  "SearchExactMatchImpressionShare","SearchImpressionShare"),
                         report="ACCOUNT_PERFORMANCE_REPORT",
                         start=ninetyDaysAgo,
                         end=yesterday)

chunk8_data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk8_body)

names(chunk8_data) <- c("Day","CPC","ISLostToRank","ISLostToBudget","ExactMatchIS","IS")

long_chunk8 <- gather(chunk8_data, metric, value, CPC:IS)

long_IS <- long_chunk8 %>% filter(metric %in% c("IS","ISLostToBudget","ISLostToRank"))
long_other <- long_chunk8 %>% filter(metric %in% c("CPC","ExactMatchIS"))

ggplot(long_other, aes(x = Day, y = value)) +
    geom_line() +
    facet_wrap(~metric, ncol=1)

ggplot(long_IS) +
    geom_area(aes(x = Day, y = value, fill = metric), position = "stack")

```

# Metrics pacing vs targets

```{r metrics pacing, echo=FALSE, eval=FALSE}

chunk9_body <- statement(select=c('Conversions','Cost'),
                         report="ACCOUNT_PERFORMANCE_REPORT",
                         start=startOfCurrentMonth,
                         end=yesterday)

chunk9_data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk9_body)

paceConv <- (targetConversions/days_in_month(today())) * day(yesterday)
paceCost <- (availableBudget/days_in_month(today())) * day(yesterday)

allStats <- data.frame(stat = c("target","pace","current"),
                       conversions = c(targetConversions, paceConv, chunk9_data$Conversions),
                       cost = c(availableBudget, paceCost, chunk9_data$Cost))

ggplot(data = allStats, aes(x = "", y = conversions, fill = stat)) +
    geom_bar(stat = "identity", position = "dodge", width = 0.2) +
    coord_flip()

ggplot(data = allStats, aes(x = "", y = cost, fill = stat)) +
    geom_bar(stat = "identity", position = "dodge", width = 0.2) +
    coord_flip()

```
