---
title: "[CLIENT NAME] AdWords Performance"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapse: true
      smooth_scroll: false
    fig_width: 8
    fig_height: 7
    fig_align: "center"
    df_print: tibble
    theme: sandstone
---

```{r setup, include=FALSE}
# Libraries
library(RAdwords)
library(lubridate)
library(ggplot2)
library(tidyverse)
library(corrplot)
library(scales)
library(tidytext)
library(cowplot)
library(httr)
library(plotly)
library(AnomalyDetection)
library(gtrendsR)
library(treemap)
library(tmap)
library(sp)
library(rgdal)
library(ggrepel)
library(rmarkdown)
library(knitr)

# Variables
googleAuth <- doAuth()
customerId <- Sys.getenv("CLIENT1ID")
availableBudget <- 30000
targetConversions <- 300

# Dates
yesterday = today() - days(1)
startOfCurrentMonth = today() - day(today()) + 1
endOfLastMonth = startOfCurrentMonth - 1 
starOfLastMonth = endOfLastMonth - days_in_month(endOfLastMonth) + 1
thirtyDaysAgo <- today() - days(30)
sixtyDaysAgo <- today() - days(60)
ninetyDaysAgo <- today() - days(90)
aYearAgo <- today() - days(365)

```

```{r data grabs, warning=FALSE, echo=FALSE, eval=TRUE}

#campaignPerformanceQuery <- statement(select=c("Date","CampaignName","Conversions","Cost"),
#                         report="CAMPAIGN_PERFORMANCE_REPORT",
#                         start=ninetyDaysAgo,
#                         end=yesterday)
#
#campaignPerformance <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=campaignPerformanceQuery)
#names(campaignPerformance) <- c("Date","Campaign", "Conversions", "Cost")

#accountPerformanceQuery <- statement(select=c("Date","DayOfWeek","HourOfDay","Device","Clicks","Impressions",
#                                         "Conversions","Cost", "SearchImpressionShare", "AveragePosition",
#                                         "SearchRankLostImpressionShare","SearchBudgetLostImpressionShare",
#                                         "SearchExactMatchImpressionShare"),
#                         report="ACCOUNT_PERFORMANCE_REPORT",
#                         start=aYearAgo,
#                         end=yesterday)
#
#accountPerformance <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=accountPerformanceQuery)
#names(accountPerformance) <- c("Date","DayOfWeek","HourOfDay","Device","Clicks","Impressions","Conversions","Cost","SearchIS",
#                               "Position","RankLostIS","BudgetLostIS","ExactMatchIS")
#
#
#chunk12Body <- statement(select=c("Date","CampaignName","AdGroupName","Criteria","Impressions","HasQualityScore","CreativeQualityScore",
#                                   "PostClickQualityScore","SearchPredictedCtr","QualityScore"),
#                         report="KEYWORDS_PERFORMANCE_REPORT",
#                         where="HasQualityScore = TRUE",
#                         start=yesterday,
#                         end=yesterday)
#
#chunk12Data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk12Body)
#
#
#chunk13Body <- statement(select=c("Date","KeywordMatchType","Impressions","Clicks","Cost","Conversions"),
#                         report="KEYWORDS_PERFORMANCE_REPORT",
#                         start=ninetyDaysAgo,
#                         end=yesterday)
#
#chunk13Data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk13Body)
#
#
#chunk15Body <- statement(select=c("Criteria","CostPerConversion","Impressions","QualityScore",
#                                   "Cost","Conversions", "AveragePosition", "AverageCpc"),
#                         report="KEYWORDS_PERFORMANCE_REPORT",
#                         start=ninetyDaysAgo,
#                         end=yesterday)
#
#chunk15Data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk15Body)
#
#chunk17Body <- statement(select=c("Criteria","Impressions","SearchImpressionShare"),
#                         report="KEYWORDS_PERFORMANCE_REPORT",
#                         start=ninetyDaysAgo,
#                         end=yesterday)
#
#chunk17Data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk17Body)
#
#
#chunk7Body <- statement(select=c("Query","Clicks","Impressions","Conversions","Cost"),
#                         report="SEARCH_QUERY_PERFORMANCE_REPORT",
#                         start=ninetyDaysAgo,
#                         end=yesterday)
#
#chunk7Data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk7Body)
#
#
#chunk11Body <- statement(select=c('EffectiveFinalUrl'),
#                         report="FINAL_URL_REPORT",
#                         where="Impressions > 0",
#                         start=ninetyDaysAgo,
#                         end=yesterday)
#
#chunk11Data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk11Body)
#
#
#chunk14Body <- statement(select=c('CampaignName','AdGroupName','Id','Description','HeadlinePart2','CriterionId',
#                                   'Cost',"Conversions","CostPerConversion"),
#                         report="AD_PERFORMANCE_REPORT",
#                         where="Cost > 100000000 AND AdNetworkType1 = SEARCH",
#                         start=ninetyDaysAgo,
#                         end=yesterday)
#
#chunk14Data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk14Body)
#
#chunk19Body <- statement(select=c("CountryCriteriaId","RegionCriteriaId","Cost","Conversions","AverageCpc", "CostPerConversion"),
#                         report="GEO_PERFORMANCE_REPORT",
#                         start=ninetyDaysAgo,
#                         end=yesterday)
#
#chunk19Data <- getData(clientCustomerId=customerId, google_auth=googleAuth, statement=chunk19Body)




```
# Campaign performance {.tabset}

```{r campaign scatterplots, echo=FALSE, results="asis", eval=FALSE}

cat("\n\n## Month-to-date\n")
campaignPerformanceMtd <- campaignPerformance %>% filter(Date >= startOfCurrentMonth) %>% group_by(Campaign) %>%
    summarize(Cost = sum(Cost), Conversions = sum(Conversions), CPA = sum(Cost)/sum(Conversions))

plot_ly(data = campaignPerformanceMtd, x = ~Cost, y = ~CPA, size = ~Conversions,
        text = ~paste("Campaign: ", Campaign, "<br>Cost: ", Cost, "<br>Conversions: ",
                      Conversions, "<br>CPA: ", CPA),
        type = "scatter", mode = "markers")

cat("\n\n## Last 30 days\n")
campaignPerformance30 <- campaignPerformance %>% filter(Date >= thirtyDaysAgo) %>% group_by(Campaign) %>%
    summarize(Cost = sum(Cost), Conversions = sum(Conversions), CPA = sum(Cost)/sum(Conversions))

plot_ly(data = campaignPerformance30, x = ~Cost, y = ~CPA, size = ~Conversions,
        text = ~paste("Campaign: ", Campaign, "<br>Cost: ", Cost, "<br>Conversions: ",
                      Conversions, "<br>CPA: ", CPA),
        type = "scatter", mode = "markers")

cat("\n\n## Last 60 days\n")
campaignPerformance60 <- campaignPerformance %>% filter(Date >= sixtyDaysAgo) %>% group_by(Campaign) %>%
    summarize(Cost = sum(Cost), Conversions = sum(Conversions), CPA = sum(Cost)/sum(Conversions))

plot_ly(data = campaignPerformance60, x = ~Cost, y = ~CPA, size = ~Conversions,
        text = ~paste("Campaign: ", Campaign, "<br>Cost: ", Cost, "<br>Conversions: ",
                      Conversions, "<br>CPA: ", CPA),
        type = "scatter", mode = "markers")

cat("\n\n## Last 90 days\n")
campaignPerformance90 <- campaignPerformance %>% filter(Date >= ninetyDaysAgo) %>% group_by(Campaign) %>%
    summarize(Cost = sum(Cost), Conversions = sum(Conversions), CPA = sum(Cost)/sum(Conversions))

plot_ly(data = campaignPerformance90, x = ~Cost, y = ~CPA, size = ~Conversions,
        text = ~paste("Campaign: ", Campaign, "<br>Cost: ", Cost, "<br>Conversions: ",
                      Conversions, "<br>CPA: ", CPA),
        type = "scatter", mode = "markers")

```

# Metrics correlation plot

```{r correlation plot, echo=FALSE, warning=FALSE, eval=FALSE}

correlationData <- accountPerformance %>% group_by(Date) %>%
    summarise(Clicks = sum(Clicks), Conversions = sum(Conversions),
              CPA = sum(Cost)/sum(Conversions), Cost = sum(Cost),
              ConversionRate = sum(Conversions)/sum(Clicks),
              CPC = sum(Cost)/sum(Clicks), Impressions = sum(Impressions),
              CTR = sum(Clicks)/sum(Impressions)) %>%
    select(Clicks, Conversions, CPA, Cost, ConversionRate, CPC, Impressions, CTR)

correlationData[!is.finite(correlationData$CPA),"CPA"] <- 0

corr <- cor(correlationData)

corrplot(corr, method = "pie", type = "upper")

```		

# Ad Scheduling Heatmaps {.tabset}

```{r ad scheduling heatmaps, echo=FALSE, results="asis", eval=FALSE}

accountPerformanceHeatmaps <- accountPerformance %>% filter(Date >= ninetyDaysAgo) %>% mutate(ImpIS = Impressions * SearchIS) %>%
    group_by(DayOfWeek,HourOfDay) %>%
    summarize(Impressions = sum(Impressions), Conversions = sum(Conversions), CPA = sum(Cost)/sum(Conversions),
              ImpIS = sum(ImpIS, na.rm=TRUE)) %>% mutate(WeightedIS = ImpIS / Impressions)

accountPerformanceHeatmaps$HourOfDay <- factor(accountPerformanceHeatmaps$HourOfDay, levels=c(0:23))
accountPerformanceHeatmaps$DayOfWeek <- factor(accountPerformanceHeatmaps$DayOfWeek,
                                         levels=c("Sunday","Saturday","Friday","Thursday","Wednesday","Tuesday","Monday"))
cat("\n\n## Impressions\n")
ggplot(accountPerformanceHeatmaps, aes(x=HourOfDay, y=DayOfWeek, z=Impressions)) + geom_tile(aes(fill = Impressions)) +
    scale_fill_gradient(low="white", high="blue", labels=comma)

cat("\n\n## Search IS\n")
ggplot(accountPerformanceHeatmaps, aes(x=HourOfDay, y=DayOfWeek, z=WeightedIS)) + geom_tile(aes(fill = WeightedIS)) +
    scale_fill_gradient(low="white", high="blue", labels=comma)

cat("\n\n## Conversions\n")
ggplot(accountPerformanceHeatmaps, aes(x=HourOfDay, y=DayOfWeek, z=Conversions)) + geom_tile(aes(fill = Conversions)) +
    scale_fill_gradient(low="white", high="blue", labels=comma)

cat("\n\n## CPA\n")
ggplot(accountPerformanceHeatmaps, aes(x=HourOfDay, y=DayOfWeek, z=CPA)) + geom_tile(aes(fill = CPA)) +
    scale_fill_gradient(low="white", high="blue", labels=comma)

```

# Search Terms N-Grams {.tabset}

```{r tidy search terms, echo=FALSE, eval=FALSE}

data(stop_words)

unigrams <- chunk7Data %>% unnest_tokens(word, Searchterm) %>% anti_join(stop_words) %>%
    group_by(word) %>%
    summarize(Clicks=sum(Clicks), Impressions=sum(Impressions), Conversions=sum(Conversions), Cost=sum(Cost),
              Ctr=sum(Clicks)/sum(Impressions), ConversionRate=sum(Conversions)/sum(Clicks), Cpa=sum(Cost)/sum(Conversions),
              AvgCpc = sum(Cost)/sum(Clicks))

bigrams <- chunk7Data %>% unnest_tokens(bigram, Searchterm, token="ngrams", n=2) %>% group_by(bigram) %>%
    summarize(Clicks=sum(Clicks), Impressions=sum(Impressions), Conversions=sum(Conversions),
              Cost=sum(Cost), Ctr=sum(Clicks)/sum(Impressions), ConversionRate=sum(Conversions)/sum(Clicks),
              Cpa=sum(Cost)/sum(Conversions), AvgCpc = sum(Cost)/sum(Clicks))

trigrams <- chunk7Data %>% unnest_tokens(trigram, Searchterm, token="ngrams", n=3) %>% group_by(trigram) %>%
    summarize(Clicks=sum(Clicks), Impressions=sum(Impressions), Conversions=sum(Conversions),
              Cost=sum(Cost), Ctr=sum(Clicks)/sum(Impressions), ConversionRate=sum(Conversions)/sum(Clicks),
              Cpa=sum(Cost)/sum(Conversions), AvgCpc = sum(Cost)/sum(Clicks))

```

## Unigrams

```{r unigrams, echo=FALSE, eval=FALSE}

pu_imp <- unigrams %>% top_n(10, Impressions) %>% ggplot(aes(y=Impressions, x=reorder(word, Impressions))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("word") +
    theme(axis.text.y = element_text(size=8))

pu_clicks <- unigrams %>% top_n(10, Clicks) %>% ggplot(aes(y=Clicks, x=reorder(word, Clicks))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("word") +
    theme(axis.text.y = element_text(size=8))

pu_ctr <- unigrams %>% filter(Clicks > 100) %>% top_n(10, Ctr) %>% ggplot(aes(y=Ctr, x=reorder(word, Ctr))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("word") +
    theme(axis.text.y = element_text(size=8))

pu_cpc <- unigrams %>% filter(Clicks > 100) %>% top_n(10, AvgCpc) %>% ggplot(aes(y=AvgCpc, x=reorder(word, AvgCpc))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("word") +
    theme(axis.text.y = element_text(size=8))

pu_cost <- unigrams %>% top_n(10, Cost) %>% ggplot(aes(y=Cost, x=reorder(word, Cost))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("word") +
    theme(axis.text.y = element_text(size=8))

pu_conv <- unigrams %>% top_n(10, Conversions) %>% ggplot(aes(y=Conversions, x=reorder(word, Conversions))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("word") +
    theme(axis.text.y = element_text(size=8))

pu_cpa <- unigrams %>% filter(Conversions > 1) %>% top_n(10, Cpa) %>% ggplot(aes(y=Cpa, x=reorder(word, Cpa))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("word") +
    theme(axis.text.y = element_text(size=8))

pu_cr <- unigrams %>% filter(Conversions > 1) %>% top_n(10, ConversionRate) %>% ggplot(aes(y=ConversionRate, x=reorder(word, ConversionRate))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("word") +
    theme(axis.text.y = element_text(size=8))

plot_grid(pu_imp, pu_clicks, pu_ctr, pu_cpc, pu_cost, pu_conv, pu_cpa, pu_cr, ncol=2)

```

## Bigrams

```{r bigrams, echo=FALSE, eval=FALSE}

pb_imp <- bigrams %>% top_n(10, Impressions) %>% ggplot(aes(y=Impressions, x=reorder(bigram, Impressions))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

pb_clicks <- bigrams %>% top_n(10, Clicks) %>% ggplot(aes(y=Clicks, x=reorder(bigram, Clicks))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

pb_ctr <- bigrams %>% filter(Clicks > 100) %>% top_n(10, Ctr) %>% ggplot(aes(y=Ctr, x=reorder(bigram, Ctr))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

pb_cpc <- bigrams %>% filter(Clicks > 100) %>% top_n(10, AvgCpc) %>% ggplot(aes(y=AvgCpc, x=reorder(bigram, AvgCpc))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

pb_cost <- bigrams %>% top_n(10, Cost) %>% ggplot(aes(y=Cost, x=reorder(bigram, Cost))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

pb_conv <- bigrams %>% top_n(10, Conversions) %>% ggplot(aes(y=Conversions, x=reorder(bigram, Conversions))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

pb_cpa <- bigrams %>% filter(Conversions > 1) %>% top_n(10, Cpa) %>% ggplot(aes(y=Cpa, x=reorder(bigram, Cpa))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

pb_cr <- bigrams %>% filter(Conversions > 1) %>% top_n(10, ConversionRate) %>% ggplot(aes(y=ConversionRate, x=reorder(bigram, ConversionRate))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

plot_grid(pb_imp, pb_clicks, pb_ctr, pb_cpc, pb_cost, pb_conv, pb_cpa, pb_cr, ncol=2)

```

## Trigrams

```{r trigrams, echo=FALSE, eval=FALSE}

pt_imp <- trigrams %>% top_n(10, Impressions) %>% ggplot(aes(y=Impressions, x=reorder(trigram, Impressions))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

pt_clicks <- trigrams %>% top_n(10, Clicks) %>% ggplot(aes(y=Clicks, x=reorder(trigram, Clicks))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

pt_ctr <- trigrams %>% filter(Clicks > 100) %>% top_n(10, Ctr) %>% ggplot(aes(y=Ctr, x=reorder(trigram, Ctr))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

pt_cpc <- trigrams %>% filter(Clicks > 100) %>% top_n(10, AvgCpc) %>% ggplot(aes(y=AvgCpc, x=reorder(trigram, AvgCpc))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

pt_cost <- trigrams %>% top_n(10, Cost) %>% ggplot(aes(y=Cost, x=reorder(trigram, Cost))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

pt_conv <- trigrams %>% top_n(10, Conversions) %>% ggplot(aes(y=Conversions, x=reorder(trigram, Conversions))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

pt_cpa <- trigrams %>% filter(Conversions > 1) %>% top_n(10, Cpa) %>% ggplot(aes(y=Cpa, x=reorder(trigram, Cpa))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

pt_cr <- trigrams %>% filter(Conversions > 1) %>% top_n(10, ConversionRate) %>% ggplot(aes(y=ConversionRate, x=reorder(trigram, ConversionRate))) +
    geom_bar(stat = "identity") +
    coord_flip() +
    xlab("phrase") +
    theme(axis.text.y = element_text(size=8))

plot_grid(pt_imp, pt_clicks, pt_ctr, pt_cpc, pt_cost, pt_conv, pt_cpa, pt_cr, ncol=2)

```

# Impression Share analysis

```{r impression share, echo=FALSE, eval=FALSE}

accountPerformanceIS <- accountPerformance %>% filter(Date >= ninetyDaysAgo) %>%
    mutate(ImpIS = Impressions * SearchIS, ImpBudgetLostIS = Impressions * BudgetLostIS,
           ImpRankLostIS = Impressions * RankLostIS,
           ImpExactMatchIS = Impressions * ExactMatchIS) %>%
    group_by(Date) %>%
    summarize(CPC = sum(Cost, na.rm = TRUE)/sum(Clicks, na.rm = TRUE), ImpRankLostIS = sum(ImpRankLostIS, na.rm = TRUE),
              ImpBudgetLostIS = sum(ImpBudgetLostIS, na.rm = TRUE), ImpIS = sum(ImpIS, na.rm=TRUE),
              ImpExactMatchIS = sum(ImpExactMatchIS, na.rm = TRUE), Impressions = sum(Impressions, na.rm = TRUE)) %>%
    mutate(IS = ImpIS / Impressions, ISLostToRank = ImpRankLostIS / Impressions,
           ISLostToBudget = ImpBudgetLostIS / Impressions,
           ExactMatchIS = ImpExactMatchIS / Impressions)

longAccountPerformanceIS <- gather(accountPerformanceIS, metric, value, CPC:ExactMatchIS)

long_IS <- longAccountPerformanceIS %>% filter(metric %in% c("IS","ISLostToBudget","ISLostToRank"))
long_other <- longAccountPerformanceIS %>% filter(metric %in% c("CPC","ExactMatchIS"))

ggplot(long_IS) +
    geom_area(aes(x = Date, y = value, fill = metric), position = "stack") +
    theme(legend.position = "bottom")

ggplot(long_other, aes(x = Date, y = value)) +
    geom_line() +
    facet_wrap(~metric, ncol=1)

```

# Metrics pacing vs targets

```{r metrics pacing, echo=FALSE, fig.height=2, eval=FALSE} 

accountPerformancePacing <- accountPerformance %>% filter(Date >= startOfCurrentMonth) %>%
    summarize(Conversions = sum(Conversions), Cost = sum(Cost))

paceConv <- (targetConversions/days_in_month(today())) * day(yesterday)
paceCost <- (availableBudget/days_in_month(today())) * day(yesterday)

allStats <- data.frame(stat = c("target","pace","current"),
                       conversions = c(targetConversions, paceConv, accountPerformancePacing$Conversions),
                       cost = c(availableBudget, paceCost, accountPerformancePacing$Cost))

ggplot(data = allStats, aes(x = stat, y = conversions, fill = stat)) +
    geom_bar(stat = "identity", position = position_dodge(0.4), width = 0.5) +
    coord_flip() +
    theme(legend.position = "none")

ggplot(data = allStats, aes(x = stat, y = cost, fill = stat)) +
    geom_bar(stat = "identity", position = position_dodge(0.4), width = 0.5) +
    coord_flip() +
    theme(legend.position = "none")

```

# Device performance

```{r device performance, echo=FALSE, eval=FALSE}

accountPerformanceDevice <- accountPerformance %>% filter(Date >= ninetyDaysAgo) %>%
    group_by(Date, Device) %>%
    summarize(Conversions = sum(Conversions, na.rm = TRUE), Cost = sum(Cost, na.rm = TRUE),
              Clicks = sum(Clicks, na.rm = TRUE),
              Impressions = sum(Impressions, na.rm = TRUE)) %>%
    mutate(CPA = Cost / Conversions, ConversionRate = Conversions / Clicks,
           CPC = Cost / Clicks, CTR = Clicks / Impressions)

longAccountPerformanceDevice <- accountPerformanceDevice %>% gather(metric, value, Conversions:CTR)

longAccountPerformanceDevice %>% ggplot(aes(x = Date, y = value, color = Device)) +
    geom_line() +
    facet_grid(metric ~ ., scales = "free_y") +
    theme(legend.position = "bottom")

```

# 404 Checker

```{r 404 checker, echo=FALSE, eval=FALSE}

responseCodes <- character()

for(i in chunk11Data$FinalURL){
    url <- as.character(i)
    response <- GET(i)
    Sys.sleep(sample(1:5, 1))
    responseCodes <- c(responseCodes, response$status_code)
}

responseCodes <- data.frame(ResponseCode = responseCodes)

problemURLs <- cbind(chunk11Data, responseCodes) %>% filter(responseCodes != 200)

if(nrow(problemURLs) == 0){
    message("All Final URLs are ok.")
}else{ problemURLs }

```

# Quality Score analysis {.tabset}

```{r quality score analysis, echo=FALSE, message=FALSE, results="asis", eval=FALSE}

cat("\n## Ad Relevance\n")
kable(chunk12Data %>% group_by(Adrelevance) %>% summarize(n = n()) %>% mutate(freq = n/sum(n)) %>% arrange(desc(n)))
cat("\n## LP Experience\n")
kable(chunk12Data %>% group_by(Landingpageexperience) %>% summarize(n = n()) %>% mutate(freq = n/sum(n)) %>% arrange(desc(n)))
cat("\n## Expected CTR\n")
kable(chunk12Data %>% group_by(Expectedclickthroughrate) %>% summarize(n = n()) %>% mutate(freq = n/sum(n)) %>% arrange(desc(n)))
cat("\n## Total QS\n")
kable(chunk12Data %>% group_by(Qualityscore) %>% summarize(n = n()) %>% mutate(freq = n/sum(n)) %>% arrange(desc(n)))

cat("\n## Weighted QS\n")
plotData <- chunk12Data %>% mutate(QSImpr = as.numeric(Qualityscore) * Impressions) %>% group_by(Campaign, Adgroup) %>%
    summarise(QSImpr = sum(QSImpr), Impressions = sum(Impressions)) %>% ungroup() %>% mutate(weightedQS = QSImpr/Impressions) 

plot <- plotData %>% ggplot(aes(x = weightedQS, y = 1)) + geom_text(aes(label = Adgroup),position = position_jitter(0.7), size = 1.5)
ggplotly(plot)

```

# Match type performance

```{r match type performance, echo=FALSE, eval=FALSE}

names(chunk13Data) <- c("Date","MatchType","Impressions","Clicks","Cost","Conversions")

chunk13Data <- chunk13Data %>% group_by(Date, MatchType) %>%
    summarize(Impressions = sum(Impressions), Clicks = sum(Clicks), Cost = sum(Cost),Conversions = sum(Conversions)) %>%
    mutate(Ctr = Clicks/Impressions, CPC = Cost/Clicks, CPA = Cost/Conversions, ConversionRate = Conversions/Clicks)

chunk13_long <- gather(chunk13Data, metric, value, Impressions:ConversionRate)

ggplot(chunk13_long, aes(y = value, x = Date, color = MatchType)) +
    geom_line() +
    facet_grid(metric ~ ., scales = "free_y") +
    theme(legend.position = "bottom")

```

# Ad/Keyword Performance

```{r adKeywords performance, echo=FALSE, message = FALSE, eval=FALSE}

names(chunk14Data) <- c("Campaign", "AdGroup", "AdId", "Description", "Headline2", "KeywordId",
                         "Cost", "Conversions", "CPA")

plot_ly(data = chunk14Data, x = ~Cost, y = ~CPA, size = ~Conversions,
            text = ~paste("Campaign: ", Campaign, "<br>AdGroup: ", AdGroup, "<br>Headline2: ",
                            Headline2, "<br>Description: ", Description ,"<br>KeywordId: ", KeywordId))

```

# 3x3 Performance Segments {.tabset}

```{r performance segments matrix, echo=FALSE, message=FALSE, eval=FALSE}

names(chunk15Data) <- c("Keyword","CPA","Impressions","QS","Cost","Conversions","Position","CPC")

```

## Converters

```{r converters matrix, echo=FALSE, message=FALSE, eval=FALSE}

hasConversions <- chunk15Data %>% filter(Conversions > 0)

plot_ly(data = hasConversions, x = ~log(Conversions), y = ~CPA, color = ~Position, size = ~Position,
        text = ~paste("Keyword: ", Keyword, "<br>Conversions: ", Conversions,
                      "<br>CPA: ", CPA, "<br>Position: ", Position))
```

## Non-converters

```{r non-converters matrix, echo=FALSE, message=FALSE, eval=FALSE}

notConverting <- chunk15Data %>% filter(Conversions == 0, Cost > 0)

plot_ly(data = notConverting, x = ~log(Cost), y = ~CPC, color = ~Position, size = ~Position,
        text = ~paste("Keyword: ", Keyword, "<br>Cost: ", Cost,
                      "<br>CPC: ", CPC, "<br>Position: ", Position))
```

## Clickless

```{r clickless matrix, echo=FALSE, message=FALSE, eval=FALSE}

clickless <- chunk15Data %>% filter(Cost == 0, Impressions > 0)

plot_ly(data = clickless, x = ~log(Impressions), y = ~QS, color = ~Position, size = ~Position, type = 'scatter',
        text = ~paste("Keyword: ", Keyword, "<br>Impressions: ", Impressions,
                      "<br>QS: ", QS, "<br>Position: ", Position))
```

# Anomaly detection {.tabset}

```{r anomaly detection, echo=FALSE, results="asis", eval=FALSE}

names(chunk16Data) <- c("Date","HourOfDay","Clicks","Conversions","CPA","CPC","SearchIS","Position")
anomalyData <- chunk16Data %>% mutate(DateTime = ymd_hms(paste0(Date," ",HourOfDay,":00:00")))
anomalyData <- anomalyData %>% arrange(DateTime)

cat("\n## Clicks\n")
anomClicks <- AnomalyDetectionTs(anomalyData[,c("DateTime","Clicks")], direction='both',
                                 plot=TRUE, e_value=TRUE, max_anoms=0.01, ylabel = "Clicks")
anomClicks$plot

cat("\n\n## Conversions\n")
anomConversions <- AnomalyDetectionTs(anomalyData[,c("DateTime","Conversions")], direction='both',
                                 plot=TRUE, e_value=TRUE, max_anoms=0.01, ylabel = "Conversions")
anomConversions$plot

cat("\n\n## CPA\n")
anomCPA <- AnomalyDetectionTs(anomalyData[,c("DateTime","CPA")], direction='both',
                                 plot=TRUE, e_value=TRUE, max_anoms=0.01, ylabel = "CPA")
anomCPA$plot

cat("\n\n## CPC\n")
anomCPC <- AnomalyDetectionTs(anomalyData[,c("DateTime","CPC")], direction='both',
                                 plot=TRUE, e_value=TRUE, max_anoms=0.01, ylabel = "CPC")
anomCPC$plot

cat("\n\n## IS\n")
anomSearchIS <- AnomalyDetectionTs(anomalyData[,c("DateTime","SearchIS")], direction='both',
                                 plot=TRUE, e_value=TRUE, max_anoms=0.01, ylabel = "SearchIS")
anomSearchIS$plot

cat("\n\n## Position\n")
anomPosition <- AnomalyDetectionTs(anomalyData[,c("DateTime","Position")], direction='both',
                                 plot=TRUE, e_value=TRUE, max_anoms=0.01, ylabel = "Position")
anomPosition$plot

``` 
# Google Trends: Top 5 keywords

```{r google trends, echo=FALSE, eval=FALSE}

names(chunk17Data) <- c("Keyword","Impressions","SearchIS")

lookupTerms <- chunk17Data %>% mutate(impVolume = Impressions / SearchIS) %>%
    arrange(desc(impVolume)) %>% head(5) %>% select(Keyword)

res <- gtrends(str_replace_all(lookupTerms[,1], "\\+",""), geo = "IE")
plot(res)

```

# Treemaps

```{r treemaps, echo=FALSE, eval=FALSE}

campaignPerformance90[!is.finite(campaignPerformance90$CPA),"CPA"] <- 0

treemap(campaignPerformance90, 
        index="Campaign",  
        vSize = "Cost",  
        vColor = "CPA",
        palette = "RdYlBu",
        type="value")

```

# Geoperformance {.tabset}

```{r geoperformance, echo=FALSE, message=FALSE, results="asis", eval=FALSE}

counties <- readOGR("misc","Census2011_Admin_Counties_generalised20m")

locationIds <- data.frame(name = c("Limerick City","Limerick County","North Tipperary","South Tipperary","Waterford City","Waterford County","Galway City","Galway County","Leitrim County","Mayo County","Roscommon County","Sligo County","Cavan County","Donegal County","Monaghan County","Carlow County","Dublin City","South Dublin","Fingal","Dún Laoghaire-Rathdown","Kildare County","Kilkenny County","Laois County","Longford County","Louth County","Meath County","Offaly County","Westmeath County","Wexford County","Wicklow County","Clare County","Cork City","Cork County","Kerry County"),
                          id = c(9047195,9069531,9047196,20493,9047198,20494,9047194,9069529,21317,20489,20491,20492,20476,20479,20488,20477,20478,9047197,9047193,9047192,20481,20482,20486,21316,21316,20487,20490,20495,20497,20496,20475,9047191,9070283,20483))

names(chunk19Data) <- c("Country","Region","Cost","Conversions","CPC","CPA")
chunk19Data$Region <- as.numeric(chunk19Data$Region)

mergedAdWords <- inner_join(chunk19Data, locationIds, by = c("Region"="id"))
mergedAdWords$name <- str_replace(mergedAdWords$name, "County (.*)", "\\1 County")

mergedForPlot <- sp::merge(counties, mergedAdWords, by.x = "COUNTYNAME", by.y = "name")

cat("\n\n## Conversions\n")
tm_shape(mergedForPlot) +
    tm_fill(col = "Conversions") +
    tm_text("COUNTYNAME")

cat("\n\n## CPC\n")
tm_shape(mergedForPlot) +
    tm_fill(col = "CPC") +
    tm_text("COUNTYNAME")

cat("\n\n## Cost\n")
tm_shape(mergedForPlot) +
    tm_fill(col = "Cost") +
    tm_text("COUNTYNAME")

cat("\n\n## CPA\n")
tm_shape(mergedForPlot) +
    tm_fill(col = "CPA") +
    tm_text("COUNTYNAME")


```
